---
title: "pull request for adding pacman support"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# implementation

The method of line `matched <- match.call(loader, call)` doesn't work with p_load, because `p_load` doesn't have the package list as the named argument.

Because all other arguments in `p_load` will be logical, supposedly be one of `True, False, T, F`, so I just scan `as.character(call)` to get the package name list.

p_load_gh is not implemented because I had some problems with using it to install some github repo. I need to use devtools anyway.

note pacman package itself will be picked up by original code no matter what:
if used pcaman::p_load, will pick up because of ::
if used library(pacman), will pick up because of library.

supported syntax

    pacman::p_load(stringr, units, install = FALSE)
    pacman::p_load(shiny, shinydashboard)

unsupported syntax
- arguments that saved in variable. 

    op <- TRUE
    pacman::p_load(shinyjs, install = op)
    pkgs <- c("dplyr", "tibble")
    pacman::p_load(pkgs, character.only = TRUE)

- similar usage for library cannot be detected with original packrat either

    pkg <- "ggmap"
    library(pkg, character.only = TRUE)

```{r exploration code used in development}
library(packrat)
file <- "/Users/xhdong/Projects/ctmm-explorations/shiny/dashboard1/app.R"
exprs <- suppressWarnings(parse(file, n = -1L))
e <- exprs[[3]]
env <- new.env(parent = emptyenv())
call <- e
packrat:::identifyPackagesUsed(e, env)

p <- "pacman::p_load(ggplot2,ctmm)"
p <- "p_load(ggplot2, install = FALSE)"
exprs <- suppressWarnings(parse(text = p, n = -1L))
e <- exprs2[[1]]
call <- e
env <- new.env(parent = emptyenv())
packrat:::identifyPackagesUsed(e, env)

s <- as.character(call)
sParas <- s[2:length(s)]
filterOut <- c("TRUE", "FALSE", "T", "F")
sParas[!sParas %in% filterOut]
```

test

sample code is put inside a Rmarkdown because they are not suitable for regular testtaht folder.

```{r}
# packrat:::fileDependencies(file)
packrat:::fileDependencies("inst/PR-360/test.Rmd")
```

## shiny deployment
if just build and reload package, shiny deployment will have error:

    Error: Unable to retrieve package records for the following packages:
    'packrat'

It's because packages either from CRAN or github, if github, must installed by devtools. And packrat is in implicit dependency.

I pushed my changes to my github repo, install packrat from there. Now everything worked, including pacman loader, and github installed packages. the install.package line doesn't hurt either.
